Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-26 02_Paper/paper.tex
fix typos.

The quality control of production processes and products is one fundamental part of the general quality management. It contains the measures and activities needed to fulfill specific quality requirements \cite{illes2017new}.
According to Illés, there are three established tools and methods of quality control \cite{illes2017new}:
The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC).   
The SPC is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes
in the quality characteristics in the production process \cite{selvamuthu2018introduction}. This method can also take place before the actual manufacturing process in form of an "off-line SPC". During the designing phase of a process or product,
off-line SPC procedueres are aiming to select and choose controllable product and process parameters to increase the quality of the outcoming product \cite{mitra2016fundamentals}.
\AP{@Lennart, last sentence is still quite confising to me}

@@

While the SPC mostly optimizes the capability of the process, for example the acceptance plan prevents the nonconforming product to be pass and then delivered to the next process or the customer \cite{kurniati2015quality}.
In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
Statistical methods are faster than hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
if the variance of the product quality is to high.
The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
by involving all departments of the organization \cite{illes2017new}.
The quality characteristics of a product can be classified as variables or attributes.
Variables are measurable characteristics, which are shown as numbers. On the contrary,
attributes are not measureable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, 
precise measured values are available, which enable precise adjustment of the process parameters. 
This allows the desired quality to be restored. With that in mind, a predictive quality control is a promising solution.

@@

PA offers a wide range of applications, and it can be implemented as long as there is enough data available. By conosidering industrial and production environment, PA would be a great asset due to the high flexibility and high amound of data available comming from processes, single machines or cells, producs, and others. Some commmon industrial applications of PA at the industry are focused products (design and optimization), machine (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.

@@

The outcome of an explorative literature review on this matter, shows that the findings that combines PA and QC are very scarce in literature. This could be in great part, due to the novelty of the area \cite{aumi2012model, ritter1992neue}. Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.

Based on an explorative literature review on this matter, the short outcome is that the findings that combines PA and QC are very scarce in literature. This could be in great part, due to computer power limitations in early researchs and the recent increase of ML applications on this area  \cite{aumi2012model, ritter1992neue}. Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.

@@

Those simulated failures have a real impact in the data collected by the sensors. Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticiable shifting on pieces' position as well as the stop of the process.

The continous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learching implementations. With this in mind, our goal is to predict the quality of the product (concentricity of the assambled parts), prior to the actual quality check done by the laser scanner. The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and high degree of scalability. This would be an step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assambled pieces.

@@

\section*{Acknowledgments}
This project was partly supported by the german and european IKT.NRW
project "`ManuBrain"' 
\DSt{
do we need to include ManuBrain reference here?
}

>>>>

The quality control of production processes and products is one fundamental part of the general quality management. It contains the measures and activities needed to fulfill specific quality requirements \cite{illes2017new}.
According to Illés, there are three established tools and methods of quality control \cite{illes2017new}:
The Statistical Process Control (SPC), Auditing and Total Quality Control (TQC).   
The SPC is normally used to monitor the production process using recorded data values for the quality characteristics, as well as to indicate any significant changes
in the quality characteristics in the production process \cite{selvamuthu2018introduction}. This method can also take place before the actual manufacturing process in form of an "off-line SPC". During the designing phase of a process or product,
off-line SPC procedures are aiming to select and choose controllable product and process parameters to increase the quality of the outcoming product \cite{mitra2016fundamentals}.
\AP{@Lennart, last sentence is still quite confusing to me}

@@

While the SPC mostly optimizes the capability of the process, for example the acceptance plan prevents the nonconforming product to be pass and then delivered to the next process or the customer \cite{kurniati2015quality}.
In the case of a hundred percent control, this is associated with higher costs and a higher requirement of time, compared to a quality control based on a machine learning model.
Statistical methods are faster than hundred percent controls, but have the same problem like the SPC: Because they are based on assumptions, this methods are prone to errors,
if the variance of the product quality is to high.
The concept of TQC is to extend the scope of quality control to the whole company and product life cycle,
by involving all departments of the organization \cite{illes2017new}.
The quality characteristics of a product can be classified as variables or attributes.
Variables are measurable characteristics, which are shown as numbers. On the contrary,
attributes are not measurable and can only take the value go or no-go \cite{mitra2016fundamentals}. 
The advantage of variable measurements is that in the event of a defective intermediate or end product, 
precise measured values are available, which enable precise adjustment of the process parameters. 
This allows the desired quality to be restored. With that in mind, predictive quality control is a promising solution.

@@

PA offers a wide range of applications, and it can be implemented as long as there is enough data available. By considering industrial and production environment, PA would be a great asset due to the high flexibility and high amound of data available coming from processes, single machines or cells, products, and others. Some common industrial applications of PA at the industry are focused products (design and optimization), machine (predictive maintenance) and production (scheduling) \cite{krauss2019machine}.

@@

The outcome of an explorative literature review on this matter, shows that the findings that combines PA and QC are very scarce in the literature. This could be in great part, due to the novelty of the area \cite{aumi2012model, ritter1992neue}. Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.

Based on an explorative literature review on this matter, the short outcome is that the findings that combine PA and QC are very scarce in the literature. This could be in great part, due to computer power limitations in early research and the recent increase of ML applications on this area  \cite{aumi2012model, ritter1992neue}. Related work, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated} and a product quality prediction in a process chain \cite{krauss2019machine}.

@@

Those simulated failures have a real impact in the data collected by the sensors. Anomalies can be observed at the vibration sensors, temperature rise, fluctuations in the air pressure system, noticeable shifting on pieces' position as well as the stop of the process.

The continous data collection and clear correlation between the machine parameter is the ideal play-ground to implement a sandbox for machine learning implementations. With this in mind, our goal is to predict the quality of the product (concentricity of the assembled parts), prior to the actual quality check done by the laser scanner. The findings gained with the demonstration cell can be transferred to various real assembly processes and use cases, due to its manageable size and a high degree of scalability. This would be an step forwards for future implementations at the industry, where the quality predictions might determine early enough, the next steps for the assembled pieces.

@@

\section*{Acknowledgments}
This project was partly supported by the German and European IKT.NRW
project "`ManuBrain"' 
\DSt{
do we need to include ManuBrain reference here?
}
